Hysteresis in human computation:\\ how one task affects another

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
little fig edit

			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
			& \multirow{2}{*}{echo} & food & food & none\\
			& & obj & objects & none\\

@@

\subsection*{S1: Experimental materials}
The tasks for both experiments were presented as a series of slides.  In
both cases, the first slide consisted of a brief set of instructions, followed
by the frame if shown (only some treatments involved a frame), see 
Fig. S\ref{fig:hit_preamble}.  Following the instructions and prime, a set
of initial tasks was shown (except for the treatments in \textit{frame2}
and \textit{echo}) followed by (in all cases) a set of test tasks.  In
\textit{exp1}, two kinds of frame were used, one simple frame, and one where
the worker was required to echo the frame using a combo-box input.  The
instructions, both kinds of frame, and an example task slide, are shown 
in Fig. S1.
\begin{figure}
	\includegraphics[scale=0.8]{figs/tasks.pdf}
	\label{fig:hit_preamble}
	\caption{Examples of A) instructions; B) a frame, as shown in 
		\textit{frame1:obj}, and similar to those shown in 
		\textit{frame1:food} and \textit{frame2:food}, and 
		\textit{frame2:cult};  
		C) an echoed frame, as used in \textit{echo:obj}, and similar to that
		used in \textit{echo:food}; and D) an 
		example of an image-labeling task.
	}
\end{figure}

@@

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{echo}} \\
		\toprule
		apple & 24 \\
		cheese & 23 \\
		wine & 15 \\
		coffee & 14 \\
		oil & 7 \\
		knife & -24 \\
		dinner & -26 \\
		fork & -27 \\
		candle & -35 \\
		food & -55 \\
		\bottomrule
		\end{tabular}

>>>>

			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
			& \multirow{2}{*}{echo1} & food & food & none\\
			& & obj & objects & none\\

@@

\subsection*{S1: Experimental materials}
The tasks for both experiments were presented as a series of slides.  In
both cases, the first slide consisted of a brief set of instructions, followed
by the frame if shown (only some treatments involved a frame), see 
Fig. S\ref{fig:hit_preamble}.  Following the instructions and prime, a set
of initial tasks was shown (except for the treatments in \textit{frame2}
and \textit{echo1}) followed by (in all cases) a set of test tasks.  In
\textit{exp1}, two kinds of frame were used, one simple frame, and one where
the worker was required to echo the frame using a combo-box input.  The
instructions, both kinds of frame, and an example task slide, are shown 
in Fig. S1.
\begin{figure}
	\includegraphics[scale=0.8]{figs/tasks.pdf}
	\label{fig:hit_preamble}
	\caption{Examples of A) instructions; B) a frame, as shown in 
		\textit{frame1:obj}, and similar to those shown in 
		\textit{frame1:food} and \textit{frame2:food}, and 
		\textit{frame2:cult};  
		C) an echoed frame, as used in \textit{echo1:obj}, and similar to that
		used in \textit{echo1:food}; and D) an 
		example of an image-labeling task.
	}
\end{figure}

@@

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{echo1}} \\
		\toprule
		apple & 24 \\
		cheese & 23 \\
		wine & 15 \\
		coffee & 14 \\
		oil & 7 \\
		knife & -24 \\
		dinner & -26 \\
		fork & -27 \\
		candle & -35 \\
		food & -55 \\
		\bottomrule
		\end{tabular}
